Seminarium TI 3700\\ Data Analysis on Twitter: An Overview

### 2014-03-26 authorinstr_2.tex
Enkele TODOs toegevoegd, moet ik nog aanpassen

\begin{abstract}
Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is data enrichment, or somehow enhancing
the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
insights into the behaviour of users on Twitter. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
for a variety of applications to be created using this information.
\end{abstract}

@@

@@

\section{Data}

@@

@@

>>>>

\begin{abstract}

%TODO: Dieper ingaan op onderwerpen, 'abstract' is enkel van toepassing op de paper, niet de onderwerpen

Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is data enrichment, or somehow enhancing
the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
insights into the behaviour of users on Twitter. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
for a variety of applications to be created using this information.
\end{abstract}

@@

%TODO: Duidelijk zeggen dat het om een survey gaat, en een duidelijke werkmethodiek introduceren

@@

\section{Before we start: Retrieving the right data}

%TODO: Duidelijk Scheiden van de rest van het onderzoek

@@

%TODO: Inhoud is goed, vorm moet gestroomlijnder doorheen hele paper. Ook moet alles vanuit onze method geschreven worden, niet vanuit de papers

@@

%TODO: Opsomming + stap naar toekomstig onderzoek maken
